### 2021-07-08 rad-icfp-2021/unf.tex
more fixes sec4

\section{UNF}
\label{sec:unf}

Following the intuition highlighted in Section~\ref{subsec:insights}, 
we present a new language which we call unary form (UNF). 
There is a Source UNF for the Source language and a Target UNF for the Target language.
Just as Target is an extension of Source, Target UNF is an extension of Source UNF.

@@

By introducing UNF, we are trying to decouple some of the problems.
UNF introduces the call-by-value evaluation of the arguments before evaluating the arguments and a good management of the environment.
Differentiation on UNF deals with the purely functional store and gradients update via pre-composition.
Finally, going back from UNF to Target uses the stored information in UNF to make sure the Jacobians are computed efficiently.

@@

The typing rules are detailed in Figure~\ref{fig:source_unf_typesystem}.
$\reals^{\times n}$ is a notation for $\reals,\ldots,\reals$ with $n$ factors $\reals$.

>>>>

\section{Unary Normal Form}
\label{sec:unf}

Following the intuition highlighted in Section~\ref{subsec:insights}, 
we present a new language which we call Unary Normal Form (UNF). 
There is a Source UNF for the Source language and a Target UNF for the Target language.
Just as Target is an extension of Source, Target UNF is an extension of Source UNF.
They serve as intermediate representation our the reverse-mode compilation pipeline (see Figure~\ref{fig:outline}).

@@

By introducing UNF, we are decoupling some of the problems.
UNF introduces the call-by-value evaluation of the arguments before evaluating the arguments and a good management of the environment.
Differentiation on UNF deals with the purely functional store and gradients update via pre-composition.
Finally, going back from UNF to Target uses the stored information in UNF to make sure the Jacobians are computed efficiently.

@@

A judgment in Source UNF is a triple !(T$_1$,e,T$_2$)! where !T$_1$! and !T$_2$! are lists of types of Source, and !e! is an expression of the Source UNF.
The typing rules are detailed in Figure~\ref{fig:source_unf_typesystem}.
$\reals^{\times n}$ is a notation for $\reals,\ldots,\reals$ with $n$ factors $\reals$. 
When !T$_1$! and !T$_2$! are lists of types and !A! a type, the operator !,! denotes snoc in !T$_1$,A! and denotes append in !T$_1$,T$_2$!.
